\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-02-09 paper.tex
move hmc
add intro paragraph for algorithm section

\dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}

Rejection sampling is the simplest ways of constrained sampling~\cite{}, but is also known for high rejection-rate on a manifold in a high-dimensional space.
Hierarchical Rejection Sampling (HRS) is thus proposed .... 
However, the rejection rate is still relatively high~\cite{}.
In this paper, we propose an informed sampling by an MCMC approach.
In order to obtained uniformly sampling on a manifold, MCMC provides an approach that samples from a high-dimensional uniform distribution subject to a manifold constraint.

\os{
Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
This is done using the concept of a canonical distribution from statistical mechanics~\cite{}. 
Given some energy function,~$E$, the canonical distribution over states has probability density function $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
Simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
}

@@

>>>>

%\dy{I am not sure what we want to put into here, but I am going to continue on the discussion of the algorithm and talk about some of the probability stuff.}

Rejection sampling is the simplest ways of constrained sampling~\cite{CRCW04}, but is also known for high rejection-rate on a manifold in a high-dimensional space~\cite{KTC16}.
Hierarchical Rejection Sampling (HRS)~\cite{KTC16} is thus proposed that sequentially samples each dimension so that an unqualified candidate can be rejected before all dimensions are sampled. 
However, the rejection rate is still relatively high~\cite{KTC16}.
In this paper, we propose an informed sampling by an MCMC approach.
In order to obtained uniformly sampling on a manifold, MCMC provides an approach that samples from a high-dimensional uniform distribution subject to a manifold constraint.
Instead of rejecting samplings, original samples are purposefully driven onto a manifold.

@@

\os{
	Roughly speaking, HMC views the system as an energy function for which Hamiltonian dynamics are simulated in fixed time steps.
	Thus, to sample from a desired distribution~$P$ using HMC, we need to convert the distribution to an energy function and vice-versa.
	This is done using the concept of a canonical distribution from statistical mechanics~\cite{N11}. 
	Given some energy function,~$E$, the canonical distribution over states has probability density function $P = \frac{1}{Z}\exp (-E/T)$, where $Z$ is a normalizing constant and $T$ is the temperature of the system.
	%Viewing this the opposite way, if we are interested in some distribution with density function $P$, we can obtain it as a canonical distribution with $T = 1$ by setting $E = -\log P - \log Z$, where $Z$ is any convenient positive constant
	Simulating Hamiltonian dynamics requires that the energy function defined is differentiable.
}
